Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-12-29 Referee1_Response_fl.tex

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noi
We thank the Reviewer for the careful read and the helpful suggestions. 
We incorporated all of the recommended changes. 
Below, we go through in detail these changes. 
\medskip

@@

\bigskip

\begin{itemize}
\item \textit{p6, l47: The sentence with ``are no longer independent'' doesn't quite make sense, given the context introduced so far in which the observations of y can be dependent.}
\end{itemize}

\noi 
Deleted this sentence. 
Thank you; good catch! 
We revised and rearranged the beginning of this paragraph for better flow.  
\medskip

\begin{itemize}
\item \textit{p11, l16: Delete extra space in \S4.4.}
\end{itemize}

\noi 
Done. 
\medskip

\begin{itemize}
\item \textit{p13, l21-22: I know what the authors mean, but I can't quite parse the last sentence of the proof of Lemma 2.}
\end{itemize}

\noi
Deleted this sentence. Shortened the paragraph as suggested by Reviewer 2. 
\medskip

\begin{itemize}
\item \textit{p13, l37: Suggest: is nearly identical to that above.}
\end{itemize}

\noindent 
Deleted this sentence as suggested by Reviewer 2. 
\medskip

\begin{itemize}
\item \textit{p17, l58: ``solving'' could be deleted so we don't have the notion of ``solving ... runs''; this may appear elsewhere, too.}
\end{itemize}

### 2014-12-29 Referee2_Response_fl.tex

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noi
We thank the Reviewer for the careful read and the helpful suggestions. 
We incorporated all of the recommended changes. 
Below, we go through in detail these changes. 
\medskip

\bigskip

\begin{itemize}
\item \textit{Page 1, Abstract: Minor suggested changes as mentioned on annotated copy.}
\end{itemize}

@@

\noi 
Done. 
\medskip

\begin{itemize}
\item \textit{2, 6 (and elsewhere): ``Active'' citations should be of the form ``Smith [2013]'', while ``passive'' (``parenthetical'') cites should be of the form ``[Smith, 2013]''.}
\end{itemize}

\noi 
Checked all and corrected as needed. 
\medskip

\begin{itemize}
\item \textit{2, 8: Minor wording suggestions as on annotated copy.}
\end{itemize}

\noindent 
Done. 
\medskip

\begin{itemize}
\item \textit{5, -3: Footnote can go in main text. Also, $\bar{\bar{y}}$ was already defined.}
\end{itemize}

\noindent  
Done. 
\medskip

\begin{itemize}
\item \textit{6, 2: Naive question: Are the $y_i$'s independent or possibly correlated in your specific problem application?}
\end{itemize}

\noi
Correlated in a particular way. 
Added a comment on this in Section 2.1.1.
\medskip

\begin{itemize}
\item \textit{7: Suggest that you include a couple of references where indicated in annotated copy.}
\end{itemize}

@@

\noi
Done. 
\medskip

\begin{itemize}
\item \textit{9, -9: Maybe mention that $x_j^*$ may not be unique.}
\end{itemize}

@@

\noi
Done.
\medskip

\begin{itemize}
\item \textit{10, 2 (and elsewhere): Save time and space by defining $n_b =\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1$.}
\end{itemize}

\noi
Done.
We used the notation $b$ (instead of $n_b$) to denote the number of batches in the general case (Section 2), and we used $b_l$ to denote the above quantity to make the dependence on $l$ explicit.  
\medskip

\begin{itemize}
\item \textit{13, 7: Not necessary to give all of the details for (ii) (since they're so similar to (i)).}
\end{itemize}

@@

\noi
Done.
\medskip

\begin{itemize}
\item \textit{14, -9: Pick other notation for ``$dt$'' looks too much like an integrator.}
\end{itemize}

\noi
Changed it to $\tau$.
\medskip

\begin{itemize}
\item \textit{16, -5: Why the ``complicated'' expression for $Z_l$?}
\end{itemize}

\noi
Simplified.
\medskip

\begin{itemize}
\item \textit{19--20: Can you combined Figs. 2 and 3?}
\end{itemize}

@@

\noi
Done.  
\medskip

\begin{itemize}
\item \textit{21, 9: ``solving overlapping batches'' sounds funny.}
\end{itemize}

\noi
Reworded.
\medskip
